Towards atomistic resolution structure of phosphatidylcholine glycerol backbone and choline headgroup at different ambient conditions\footnote{Publication about results presented in the NMRlipids project}

### 2015-05-07 HGmodelMANUSCRIPT/coverLETTER.tex
update cover letter

Please find attached to this message a manuscript that we would like to submit for publication 
in \textit{Journal of the american chemical society} (JACS): 
`Towards atomistic resolution structure of phosphatidylcholine glycerol backbone and choline headgroup at different ambient conditions', 
by A. Botan et al. In the manuscript we combine extensive amount of experimental Nuclear Magnetic Resonance (NMR)
and molecular dynamics simulation data to understand the atomistic resolution structure of phospholipid molecules and their assemblies.

>>>>

Please find attached to this message a manuscript that we would like to submit for publication 
in \textit{Journal of the american chemical society} (JACS): 
`Towards atomistic resolution structure of phosphatidylcholine glycerol backbone and choline headgroup at different ambient conditions', 
by A. Botan et al. In the manuscript we combine extensive amount of experimental Nuclear Magnetic Resonance (NMR)
and molecular dynamics simulation data to understand the atomistic resolution structure of biologically abundant 
phospholipid molecules and their assemblies.
